---
title: "Getting started with ccfdata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with ccfdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(eval = FALSE, comment = "#>")
```

`ccfdata` is the R client for the Canadian Climate Framing data
platform — 250 000+ Canadian newspaper articles (1978–2024), 9.2 M
sentences, and 67 climate-coverage annotations.

## Setting up

Generate an API token at <https://data.ccf-project.ca> (Profile page),
then:

```{r}
library(ccfdata)
Sys.setenv(CCF_TOKEN = "eyJhbG...")   # or pass token = directly
ccf <- ccf_client()
ccf_me(ccf)
```

`ccf_me()` shows your tier and remaining quotas. Five tiers exist
(`metadata` < `analyst` < `researcher` < `expert` < `writer`); each
unlocks more endpoints and ships with a daily request budget. The
client surfaces every quota header through `ccf_last_status(ccf)`.

## Exploring the corpus

```{r}
ccf_summary(ccf)                   # corpus-level totals
ccf_articles_by_year(ccf)          # tibble: year, count
ccf_geo_data(ccf)                  # by-province aggregates
```

The 67-category annotation framework ships with the package — no
network needed:

```{r}
ccf_codebook_df()
ccf_define("sci_skepticism")
ccf_subcategories_of("economic")
```

## Time series and distributions

```{r}
library(ggplot2)

df <- ccf_distribution(
  ccf,
  columns  = c("economic_frame", "health_frame", "environmental_frame"),
  group_by = "year", lang = "en"
)

# Pivot for plotting
long <- tidyr::pivot_longer(df,
  cols = c(economic_frame, health_frame, environmental_frame),
  names_to = "frame", values_to = "n_sentences"
)

ggplot(long, aes(year, n_sentences, color = frame)) +
  geom_line() +
  labs(title = "Frame coverage over time")
```

## Searching the corpus

```{r}
hits <- ccf_search(ccf, "carbon tax",
                    level = "sentence",
                    filters = list(lang = "en", date_from = "2015-01-01"),
                    limit = 500)

# What's the per-year breakdown of those hits?
ccf_search_summary(ccf, "carbon tax", filters = list(lang = "en"))
```

For semantically similar passages, use the FAISS index:

```{r}
ccf_semantic_search(ccf, "climate refugees in the Arctic", k = 500)
```

## Cross-year cascades and events

The CCF platform identifies "cascades" — bursts of correlated coverage
across newspapers — and event clusters. Both are searchable:

```{r}
ccf_cascades_summary(ccf)
ccf_cascades_cross_year_all(ccf)
ccf_events_clusters(ccf, year_min = 2018L,
                    types = c("evt_weather"), limit = 200)
ccf_events_semantic_search(ccf, "wildfire smoke")
```

## Handling errors

The client uses typed R conditions for the most common server
responses:

```{r}
tryCatch(
  ccf_search(ccf, "carbon tax"),
  ccf_tier_error = function(e) {
    message("Need tier ", e$body$required_tier)
  },
  ccf_quota_error = function(e) {
    message("Hit quota: ", e$body$reason)
  }
)
```
